---
title: "zillow by Xiaodan"
author: "Xiaodan Chen"
date: "2017Äê12ÔÂ28ÈÕ"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##1.Define Problem
####Given new data to predict its logerror, which is the log of estimated house price minus the log of real sales price.


##2.Clean Data
```{r}
#load data
setwd("F:/tiger/zillow")
train<-read.csv('train_property.csv',stringsAsFactors = F)

#remove variables with missing values more than 20%
NA_rate<-colMeans(sapply(train,is.na))
remain_col<-names(train)[which(NA_rate<.2)]
train2<-train[,remain_col]
train2<-train2[,-1]
#remained variables
names(train2)
head(train2)
```

```{r}
#missing rate of the remained variables from the highest to the lowest
miss<-data.frame(var=remain_col,NA_rate=NA_rate[remain_col],row.names = NULL,stringsAsFactors = F)
miss<-miss[order(miss$NA_rate,decreasing = T),]
library(ggplot2)
ggplot(miss,aes(x=reorder(var,-NA_rate),y=NA_rate))+geom_bar(stat='identity',fill='red')+
  labs(x='remained variables',title='missing rate of the remained variables')+
  theme(axis.text.x = element_text(angle=90,hjust=1))
```

```{r}
str(train2)
```
##3.Explore data

The original train dataset has 90275 observations and 61 variables. After removing data with missing rate more than 20%, 31 variables are remained.

Among these 31 variables, 18 are continuous variables. Except the outcome variablE logerror, the other 17 variables can be grouped into 5 categories.

1) room count related variables: bathroomcnt, bedroomcnt, caculatedbathnbr, fullbathcnt, roomcnt

2) house size related variables: calculatedfinishedsquarefeet, finishedsquarefeet12, lotsizesquarefeet

3) house location related: longitute, latitute

4)house value related: taxvaluedollarcnt, landtaxvaluedollarcnt,  taxamount,structuretaxvaluedollarcnt

5) date related:  yearbuilt, transactiondate , assessmentyear



There are 13 categorical variables:
1) parcelid

2) house adress related: fips, regionidcity, regionidcounty, regionidzip

3) house feature related: hashottuborspa, fireplaceflag

4) property use variable: propertycountylandusecode, propertyzoningdesc,  propertylandusetypeid

5) tax : taxdelinquencyflag

6) census track and block variables: censustractandblock and rawcensustractandblock


##3.1 Univariate analysis
####3.11 the outcome variable: logerror
```{r}
summary(train2$logerror)
plot(density(train2$logerror),main='logerror')
```
Findings: in general, the logerror between estimated house price and the actual sale price is very small


####3.12 Continuous variable
Roomcount related

```{r}
names(train2)
summary(train2[,c(4,5,6,10,22)])
```

```{r}
par(mfrow=c(2,3))
hist(train2[,4],xlab='bathroomcnt',main='number of bathroom')
hist(train2[,5],xlab='bedroomcnt',main='number of bedroom')
hist(train2[,6],xlab='calculatedbathnbr',main='number of calculatedbathnbr')
hist(train2[,10],xlab='fullbathcnt',main='number o fullbathcnt')
hist(train2[,22],xlab='roomcnt',main='number of roomcnt')
```
Findings: 
1) the distribution of bathroom and bedroom are positively skewed
2) most houses have less than 5 bedroom and bathrooms
3) apart from some houses with only one room, a lot of houses have 5~8 rooms in total
4) bathroomcnt, bedroomcnt and roomcnt have better data quality cuz they do not have NAs

####House size related
```{r}
summary(train2[,c(7,8,14)])
par(mfrow=c(1,3))
hist(train2[,7],xlab='calculatedfinishedsquarefeet',main='calculatedfinishedsquarefeet')
hist(train2[,8],xlab='finishedsquarefeet12',main='finishedsquarefeet12')
hist(train2[,14],xlab='lotsizesquarefeet',main='area of the lot')

```

####House location related variables
```{r}
summary(train2[,c(12,13)])
par(mfrow=c(1,2))
hist(train2[,12],main='latitute')
hist(train2[,13],main='longtitue')
```


####House value related variables
```{r}
summary(train2[,c(25,26,28,29)])
par(mfrow=c(2,2))
hist(train2[,25],xlab='structuretaxvaluedollarcnt',main='structure tax value')
hist(train2[,26],xlab='taxvaluedollarcnt',main='total tax')
hist(train2[,28],xlab='landtaxvaluedollarcnt',main='land tax')
hist(train2[,28],xlab='taxamount',main='tax assesed for the year')

```
####Date variables
```{r}
#convert transactiondate from character to date format and create a new variable transdate to store it
train2$transDate<-as.Date(train2$transactiondate,'%Y-%m-%d')
summary(train2[,c(23,27,32)])
str(train2[,c(23,27,32)])

```

```{r}
par(mfrow=c(1,2))
hist(train2[,23],xlab='yearbuilt',main='yearbuilt')
hist(train2[,32],xlab='transDate',main='transDate',breaks='months')
```

####3.1.3categorical variables
House adress related variables
```{r}
#fips distribution
table(train2$fips)/nrow(train2)
#6037 for LA county, 6059 for Orange county and 6111 for ventura
```

```{r}
#city distribution
#table(train2$regionidcity)

#county distribution
#table(train2$regionidcounty)

#zip
#table(train2$regionidzip)
```

####House feature variable
```{r}
table(train2$hashottuborspa)/nrow(train2)
table(train2$fireplaceflag)/nrow(train2)

```

Findings: very few houses have fireplace or spa tub

####propertyuse variable
```{r}
table(train2$propertycountylandusecode)

```


```{r}
#table(train2$propertyzoningdesc)
```

####tax related
```{r}
table(train2$taxdelinquencyflag)/nrow(train2)

```
Findings:2% of the houses have tax delinquency

##3.2 Bivariate analysis
####3.2.1 continuous vs outcome
```{r}
corr<-cor(train2[,c(2,4:8,10,12:14,22,23,25,26,28,29)],use='pairwise.complete.obs')
library(corrplot)
corrplot(corr)


```


```{r}
cor_logerror<-sort(corr[,1],decreasing = T)
cor_logerror

#corelations are all soooo weak

```

```{r}
#show corelation between each variable and the logerror
par(mfrow=c(4,2))
plot(train2$finishedsquarefeet12,train2$logerror)
plot(train2$calculatedfinishedsquarefeet,train2$logerror)
plot(train2$calculatedbathnbr,train2$logerror)
plot(train2$fullbathcnt,train2$logerror)
plot(train2$bathroomcnt,train2$logerror)
plot(train2$bedroomcnt,train2$logerror)
plot(train2$structuretaxvaluedollarcnt,train2$logerror)

```
the points are randomly scattered and indicates the corelation is weak

####correlation between the transDate and the logerror
```{r}
library(lattice)
train2$transMonth<-sapply(strsplit(train2$transactiondate,'-'),function(x) x[2])
bwplot(logerror~transMonth,data=train2,xlab='month')
bwplot(logerror[which(abs(logerror)<0.05)]~transMonth,data=train2,xlab='month')
```


```{r}
err.month<-by(train2,train2$transMonth,function(x){return(mean(x$logerror))})
plot(names(err.month),err.month,type='l',xlab='month',ylab='average error')
```


Findings: distributon of logerror is similar, but average logerror differs in the month of april, may, june

####transaction day with logerror
```{r}
train2$transDay<-sapply(strsplit(train2$transactiondate,'-'),function(x) x[3])
err.day<-by(train2,train2$transDay,function(x){return(mean(x$logerror))})
plot(names(err.day),err.day,type='l',xlab='day',ylab='average logerror')
```


####3.2.2categorical variables vs outcome
For categorical variables , I would explore the relationship between the logerror and the fips, hashottuborspa,fireplaceflag,propertylanusetypeid, taxdelinquency
```{r}
library(lattice)
library(gridExtra)
fipsPlot1<-bwplot(logerror~as.character(fips),data=train2,xlab='fips')
fipsPlot2<-bwplot(logerror~as.character(fips),data=subset(train2,abs(logerror)<.05),
                  xlab='fips with logerror less than 0.05')
grid.arrange(fipsPlot1,fipsPlot2,ncol=2)

```



```{r}
spaPlot1<-bwplot(logerror~hashottuborspa,data=train2,xlab='hashottuborspa')
spaPlot2<-bwplot(logerror~hashottuborspa,data=subset(train2,abs(logerror)<.05),
                  xlab='hashottuborspa with logerror less than 0.05')
grid.arrange(spaPlot1,spaPlot2,ncol=2)
```

```{r}
firePlot1<-bwplot(logerror~fireplaceflag,data=train2,xlab='fireplaceflag')
firePlot2<-bwplot(logerror~fireplaceflag,data=subset(train2,abs(logerror)<.05),
                                                     xlab='fireplace with logerror less tha 0.05')
grid.arrange(firePlot1,firePlot2,ncol=2)



```



```{r}
taxPlot1<-bwplot(logerror~taxdelinquencyflag,data=train2,xlab='taxdelinquency')
taxPlot2<-bwplot(logerror~taxdelinquencyflag,data=subset(train2,abs(logerror)<.05),
                              xlab='taxdelinquency with logerror less tha 0.05')
grid.arrange(taxPlot1,taxPlot2,ncol=2)

```


```{r}
landPlot1<-bwplot(logerror~as.character(propertylandusetypeid),data=train2,xlab='landtype')
landPlot2<-bwplot(logerror~as.character(propertylandusetypeid),data=subset(train2,abs(logerror)<.05),
                              xlab='landtype with logerror less tha 0.05')
grid.arrange(landPlot1,landPlot2,ncol=2)

```

```{r}
anova(with(train2,lm(logerror~as.character(fips))))
```
```{r}
anova(with(train2,lm(logerror~as.character(propertylandusetypeid))))
```

```{r}
anova(with(train2,lm(logerror~hashottuborspa)))
```

```{r}
anova(with(train2,lm(logerror~fireplaceflag)))

```

```{r}
anova(with(train2,lm(logerror~taxdelinquencyflag)))
```
Findings: taxdelinquence, fips and propertylandusetypeid really matters

####3.2.3 create new variables
number of houses sold by city
```{r}
#calculate the number of houses sold by city
library(plyr)
house.city<-ddply(train2,.(regionidcity),summarise,cityhousecnt=length(regionidcity))

train3<-merge(train2,house.city,by='regionidcity',all.x=T)

with(train3,plot(cityhousecnt,logerror,main='logerror vs city house count' ))


```

```{r}
train3_sub<-train3[train3$cityhousecnt != max(train3$cityhousecnt),]
with(train3_sub,plot(cityhousecnt,logerror))
```
####number of house sold by zip
```{r}
house.zip<-ddply(train2,.(regionidzip),summarise,ziphousecnt=length(regionidzip))

train4<-merge(train2,house.zip,by='regionidzip',all.x=T)

with(train4,plot(ziphousecnt,logerror,main='logerror vs zip house count' ))

cor(train4$ziphousecnt,train$logerror)
```


####community quality
```{r}
price.zip<-ddply(train4,.(regionidzip),summarize,avgtax=mean(taxamount,na.rm = T))
train5<-merge(train4,price.zip,by='regionidzip',all.x=T)

with(train5,plot(avgtax,logerror,main='avgtax vs error ' ))



```

